Stack Safety is a Security Property

### 2021-04-17 tex/main.tex
through 9

We have shown how our properties apply to an extremely simple
subroutine model and validated them through randomized testing.
But what about more realistic systems? We now demonstrate the
flexibility of these core concepts as we extend
the core concepts of stack safety to a system that models the passing of
parameters on the stack, and then to a very simple coroutine model.

@@

\paragraph{Formalization of variable passing.}
We add extra information to our call
annotations to reflect that they may now pass variables on the stack, and that the locations
of those variables may be dynamic (as in the case of pass-by-reference).
A call annotation now includes a predicate relating machine states to the components
that should be passed---when passing by value, this will typically be freshly allocated
cells at the top of the frame, while passing by reference just gives the
addresses of the appropriate variables relative to the stack pointer.
\apt{This still doesn't make sense to me. We cannot
  give a static annotation that identifies the absolute address of a stack-allocated variable!
  Only sp-relative addresses make sense.}\leo{Better now? :)}

>>>>

We have shown how our properties apply to an extremely simple
subroutine model and validated them through randomized testing.
But what about more realistic systems? We now demonstrate the
flexibility of our core concepts by extending 
them to a system that models the passing of
parameters on the stack, and then to a very simple coroutine model.

@@

\paragraph{Formalization of variable passing.}
We add extra information to our call
annotations to reflect that they may now pass variables on the stack, and that the locations
of those variables may be dynamic (as in the case of pass-by-reference).
A call annotation now includes a predicate relating machine states to the components
that should be passed---when passing by value, this will typically be freshly allocated
cells at the top of the frame, while passing by reference just gives the
addresses of the appropriate variables relative to the stack pointer.
\apt{This still doesn't make sense to me. We cannot
  give a static annotation that identifies the absolute address of a stack-allocated variable!
  Only sp-relative addresses make sense.}\leo{Better now? :)}\apt{no: the definition of $P$ is still
  bogus. It needs to be something like a relation between  $M$ and a set of SP offsets.}
